---
title: "datamaticshtml"
author: "bhavesh"
date: "21 June 2017"
output:
  html_document: default
---

#As our data is in "xlsx" file, installing xlsx package to read the data. Also verifying the installation.

```{r}
install.packages("xlsx")
any(grepl("xlsx",installed.packages()))
```


#Now Reading data, as our required data is in sheet 2, reading sheet 2 into "datasem" candidate on seminar 04-june

```{r}
library("xlsx")
datasem<-read.xlsx("data.xlsx", sheetIndex = 2, startRow = 1, endRow = 45, header = TRUE)
datasem
```


#creating dotchart which says candidate belongs to which category in terms of experience
```{r, INCLUDE = FALSE}
library(stats)
attach(datasem)
xpr1<-(datasem$Exp)
m<-mean(xpr1, na.rm = TRUE)
m
#d1<-dotchart(xpr1,labels = "Seminar on 04 June", xlab = "Experience in Years", ylab = "Candidates", bg = par("bg"))
#d1
```

#reading data from sheet 3, seminar on 10-june

```{r}
datasem2<-read.xlsx("data.xlsx", sheetIndex = 3, startRow = 1, endRow = 12, header = TRUE)
datasem2
```

```{r}
attach(datasem2)
xpr2<-(datasem2$Exp)
d2<-dotchart(xpr2, labels = "Seminar on 10th June", xlab = "Experience in Years", ylab = "Candidates")
d2
```


# comparison graph between number of candidates belong to number experience in two seminars 
```{r}
par(mfrow=c(2,1))
dotchart(xpr1,labels = "Seminar on 04 June", xlab = "Experience in Years", ylab = "C", bg = par("bg"))
dotchart(xpr2, labels = "Seminar on 10th June", xlab = "Experience in Years", ylab = "C")
```


#categorical data
```{r}
datasem3<-read.xlsx("data.xlsx", sheetIndex = 2, startRow = 1, endRow = 45, colIndex = 6, header = TRUE)
datasem3m<-table(datasem3)
datasem3m
hist(datasem3m)
```

